### 2016-12-01 Detector/Detector.tex
Fixing up another comment on the detector chapter

When a high energy electron or photon enters a crystal, it starts a
shower producing a cascade of lower energy particles. Electrons lose
energy through bremsstrahlung, with photons undergoing $\Pe^+ \Pe^-$ 
pair production. The shower continues until the photon energy drops below the 
$\Pe^+\Pe^-$ pair production threshold, and ionisation 
starts to dominate for electrons. The shower ionises [IS THIS WHAT HAPPENS?] the atoms in the lead-tungstate
crystals, which then emit scintillation light that is converted to a current by the 
photodetectors. To record the light of the crystals, amplifying photodetectors need
to be used, with avalanche photodiodes used in the barrel region, and vacuum phototriodes employed
in the endcaps.
As the crystals are 25.8 radiation lengths long, most of the shower
is contained inside them.

@@

In the barrel region the \ac{HB}, limited in radius by the magnet coil, provides
coverage up to $|\eta|<1.3$. Beyond this $\eta$ range the \ac{HE} covers
the region up to $|\eta|<3$. The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The brass used as 
absorber fits the constraints imposed by the environment due to its short interaction length
of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range. The light from each tile is collected with a wavelength-shifting fibre, 
which is read out using hybrid photodiodes.

@@

To obtain precise muon momentum resolution, information from 
the tracker hits has to be combined with measurements in the
muon stations. The momentum resolution of the muon system
alone is 9\% for muons with \pT~up to 200 GeV, and varies with $\eta$ 
between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}. ADD FORMULA

>>>>

When a high energy electron or photon enters a crystal, it starts a
shower producing a cascade of lower energy particles. Electrons lose
energy through bremsstrahlung, with photons undergoing $\Pe^+ \Pe^-$ 
pair production. The shower continues until the photon energy drops below the 
$\Pe^+\Pe^-$ pair production threshold, and ionisation 
starts to dominate for electrons. The shower excites the atoms in the lead-tungstate
crystals, which then emit scintillation light that is converted to a current by the 
photodetectors. To record the light of the crystals, amplifying photodetectors need
to be used, with avalanche photodiodes used in the barrel region, and vacuum phototriodes employed
in the endcaps. %Because of the larger radiation levels in the endcaps
As the crystals are 25.8 radiation lengths long, most of the shower
is contained inside them.

@@

In the barrel region the \ac{HB}, limited in radius by the magnet coil, provides
coverage up to $|\eta|<1.3$. Beyond this $\eta$ range the \ac{HE} covers
the region up to $|\eta|<3$. The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The brass used as 
absorber fits the constraints imposed by the environment due to its short interaction length
%Nuclear interaction length is the mean path length required to reduce the numbers of relativistic charged particles by the factor 1/e, or 0.368, as they pass through matter.
%Nuclear interaction length is the mean distance travelled by a hadronic particle before undergoing an inelastic nuclear interaction.
of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range. The light from each tile is collected with a wavelength-shifting fibre, 
which is read out using hybrid photodiodes.

@@

To obtain precise muon momentum resolution, information from 
the tracker hits has to be combined with measurements in the
muon stations. The momentum resolution of the muon system
alone is 9\% for muons with \pT~up to 200 GeV, and varies with $\eta$ 
between 15-40\% for muons with \pT~of 1 TeV \cite{cms-jinst}. %ADD FORMULA
